---
title: "Land Use Change"
author: "Fox Redmond"
date: "`r Sys.Date()`"
output:
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r setup, include=FALSE}

#Set default chunk settings to not show background code - only output

knitr::opts_chunk$set(echo = FALSE)
```


```{r, message = FALSE}

#Load Libraries & Datasets

library(ggplot2)
library(dplyr)
library(tidyr)
library(readr) 
library(plotly)

url <- 'https://ourworldindata.org/grapher/total-agricultural-area-over-the-long-term.csv?v=1&csvType=full&useColumnShortNames=true'

land <- read_csv(url)


url2 <- 'https://ourworldindata.org/grapher/land-use-protein-poore.csv?v=1&csvType=full&useColumnShortNames=true'
crops <- read_csv(url2)

url3 <- 'https://ourworldindata.org/grapher/grazing-land-use-over-the-long-term.csv?v=1&csvType=full&useColumnShortNames=true'

grazing <- read_csv(url3)

url4 <- 'https://ourworldindata.org/grapher/total-agricultural-land-use-per-person.csv?v=1&csvType=full&useColumnShortNames=true'

landuse_cap <- read_csv(url4)

url5 <- 'https://ourworldindata.org/grapher/land-use-over-the-long-term.csv?v=1&csvType=full&useColumnShortNames=true'

longland <- read_csv(url5)

```  

### Why Care About Land Use?

<font size="5">

According to the World Wildlife Fund, 17% of the largest forest on Earth, the Amazon, has been destroyed, with almost all cleared land being used for some form of agriculture. 

&nbsp;

Land use change is one of the largest contributors to climate change on our planet. As we replace natural ecosystems with our agriculture systems, we both reduce the trees and other plants which absorb co2 from our atmosphere and increase livestock-based methane production.

&nbsp;

Among the United Nation's Sustainable Development Goals, goal 13 is Climate Action. Taking climate action to mitigate climate change involves setting up pathways to sustainably reduce global greenhouse gas emissions.

In order to address the U.N. Goal 13: Climate Action, we must first explore and better understand our state of land use change. 


### The Current Landscape

```{r}

#Set up a graph of global change in grazing land over time

longlandi <-
  longland %>% 
  filter(entity %in% 'World') %>% 
  filter(year >=1600) %>% 
  mutate(grazing_c = grazing_c/1000000)
 

ggplot(longlandi,
       aes(
         x = year,
         y = grazing_c))+
  geom_path(size =2, color = 'blue') +
  theme_bw() +
  labs(title = "The Global Spike in Grazing Land Use",
       caption = "Figure 1. Since 1600 there has been a drastic increase in global grazing/pasture land use.\n This trend tapered in 2000 and has been slightly decreasing since.",
       x = "Year",
       y = "Grazing Land Use (Millions of Hectares)")
  
```

--- 

In order to feed a growing population, the world has dedicated more of its land resources to grazing pasture land to raise livestock used to feed ourselves. According to the data's source, *Our World in Data*, grazing/pasture land means "land used permanently (five years or more) to grow herbaceous forage crops."


### A Closer Breakdown
  
```{r}

# Set up a graph of global change in pasture land - in most prominent regions - over time.

grazi <- 
  grazing %>% 
  filter(entity %in% c('North America', 'China', 'Oceania', 'Africa', 'Brazil')) %>% 
filter(year >=1600) %>% 
  mutate(grazing_c = grazing_c/1000000)
  

ggplot(grazi,
      aes( 
      x= year,
      y= grazing_c,
      color = entity)) +
  geom_path(size =1) +
  facet_wrap(~entity) +
  theme_bw() +
  labs(title = "The Spike in Grazing Land is Attributed to Several Regions",
       caption = "Figure 2. This Figure shows world regions with some of the largest increases\n in grazing land since 1600.",
       x = "Year",
       y = "Grazing Land Use (Millions of Hectares)") +
  theme(axis.text.x = element_text(angle = 55, hjust = 1))
```

---

These 5 regions have exceptionally large increases in dedicated pasture land. This is mostly due to rapidly growing populations, and/or the relative luxury to have ample available land for livestock rearing.

### The Big Question

<font size="7">

So what happens when we we add the most populous country in the world to these graphs?


### India Case Study


```{r}

# Add India to the proceeding graph to highlight a comparison

grazi2 <- 
  grazing %>% 
  filter(entity %in% c('North America', 'China', 'Oceania', 'Africa', 'Brazil', 'India')) %>% 
filter(year >=1600) %>% 
  mutate(grazing_c = grazing_c/1000000)


interactive <-
  ggplot(grazi2,
      aes( 
      x= year,
      y= grazing_c,
      color = entity)) +
  geom_path(size =1) +
  facet_wrap(~entity) +
  theme_bw() +
  labs(title = "India Does Not Following the Overarching Grazing Trend",
       caption = "Figure 3. This Figure demonstrates that India has not experienced \n rapid expansion of grazing land at all similar to other world regions.",
       x = "Year",
       y = "Grazing Land Use (Millions of Hectares)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggplotly(interactive)
```

---

Although India is the largest country in the world by population, they have significantly less land dedicated to pastures and grazing. A large part of this has to do with India's nearly 80% Hindu population. In Hinduism, cows are considered sacred animals, and therefore there is considerably less demand for their meat. Lower demand for cattle means less pasture space needed to raise them.  



### India vs. Australia


```{r}

# Recreate the preceeding graph pulling only India and Australia to explain the narrative

grazi3 <- 
  grazing %>% 
  filter(entity %in% c('Australia', 'India')) %>% 
filter(year >=1600) %>% 
  mutate(grazing_c = grazing_c/1000000)


ggplot(grazi3,
      aes( 
      x= year,
      y= grazing_c,
      color = entity)) +
  geom_path(size = 2) +
  facet_wrap(~entity) +
  theme_bw() +
  labs(title = "Australia Uses Significantly More Grazing Land than India",
       caption = "Figure 4. This figures demonstrates Australia rapid growth in grazing land \nbeginning in the early 1800s compared to India's overall little relative grazing land use.",
       x = "Year",
       y = "Grazing Land Use (Millions of Hectares)")

```

---

These graphs highlight the differences in grazing use in India (a country that does not produce
much beef) compared to Australia (a country that does produce extensive beef). It is clear that there is a correlation between beef production and required pasture land, but on the upcoming slides we will take this one step further.

### India vs. Australia

```{r}

# Make a graph to compare the total agricultural land use between India and Australia

landi <- 
  land %>% 
  filter(entity %in% c('Australia', 'India')) %>% 
filter(year >=1600) %>% 
  mutate(grazing_c = agriculture_c/1000000)


ggplot(landi,
      aes( 
      x= year,
      y= grazing_c,
      color = entity)) +
  geom_path(size = 2) +
  facet_wrap(~entity) +
  theme_bw() +
  labs(title = "Grazing Land Use Drives Agricultral Land Use",
       caption = "Figure 5. This Figure adds on to Figure 4, now including both countries total \n aggricultural land. It demonstrates how grazing land outweighs farming land \n when it comes to land requirement.",
       x = "Year",
       y = "Agricultural - Pasture & Farmland - Land Use (Millions of Hectares)")
```

---

This graph exemplifies how much more land is required to rear livestock than to grow food on farms. Even when all of India's agricultural food production is factored in, India still use significantly less agricultural land than Australia because they have so much less dedicated pastureland.


### India vs. Australia


```{r}

# Make a graph to compare total aggricultural land use per capita between Australia and India

landuse_capi2 <- 
  landuse_cap %>% 
  filter(entity %in% c('Australia', 'India')) %>% 
  filter(year >=1600)

ggplot(landuse_capi2,
       aes(
         x=year,
         y=agriculture_c_per_capita,
         color = entity)) +
  geom_path(size = 2) +
  theme_bw() +
  labs(title = "Aggricultural Land Use Dictates Efficiency",
       caption = "Figure 6. This graph takes figure 5 and accounts for each country's population",
       x = "Year",
       y = "Agricultural Land per Capita (Hectares)")
```

---

Agricultural Land per Capita denotes how much land must be dedicated towards agricultural for every person in a country. This could be viewed as a country's agricultural efficiency. However, it is important to note that food inequality must also be taken into account. Although India produces a high quantity of food, they have much higher hunger rates than Australia.


### How Countries can reduce grazing land

```{r}

# Make a graph to compare land requirements for different food sources

cropi <-
  crops %>% 
filter(entity %in% c('Tofu', 'Beef (beef herd)', 'Lamb & Mutton', 'Pig Meat', 'Rice', 'Root Vegetables'))

ggplot(cropi, 
       aes(
         x= entity, 
         y= land_use_per_100g_protein,
         fill= entity)) +
  geom_col() +
  scale_x_discrete(labels = c("Beef", "Lamb & Mutton", "Pork", "Rice", "Root Vegetables", "Tofu")) +
  theme_bw() +
  labs(title = "Red Meats are the Most Land-requiring Protein Sources",
       caption = "Figure 7. Highlights comparison in land use from key food sources.",
       x = "Food source",
       y = "Land Use (m² per 100g of protein)") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
   geom_hline(yintercept = 110, lty=2) +
   annotate(geom='text',
           x= 'Root Vegetables', 118, 
           label= '50x Soy Land Use') 
```

---

An agricultural shift away from meat sources such as beef, lamb, and mutton would greatly reduce the land the countries must use to raise livestock. Food reliancy could shift to lower land-cost meats such as pig and poultry or to even more efficient plant based proteins. This in turn could reduce the effects of land use change, allowing for the restoration of natural ecosystems, all while mitigating climate change.

### What Now?

<font size="5">

The global spike in grazing land use since 1600 has seen large portions of regions' natural ecosystem be wiped out to raise livestock. However, as we have seen, humans have much more efficient options for producing food sources. With soy proteins like Tofu taking 80-90 times less land use than Beef, Lamb and Mutton. 

&nbsp;
&nbsp;


In order to address land use changes' contribution to global climate change, we must reconsider what we use to feed ourselves in order to minimize required land.


### Data Sources

<font size="5">

All data from this story is sourced from *Our World in Data*. OWID is an organization that uses a worldwide network of researchers who publish stories with the goal of making their insights on some of the biggest global issues, more easily digestible. 


&nbsp;

Click on the following links to learn more about each of the datasets:

&nbsp;

1. [Long Term Global Land Use](https://ourworldindata.org/grapher/land-use-over-the-long-term)

2. [Long Term Grazing Land Use](https://ourworldindata.org/grapher/grazing-land-use-over-the-long-term)

3. [Long Term Agricultural Land Use](https://ourworldindata.org/grapher/total-agricultural-area-over-the-long-term)

3. [Agricultural Land Use Per Capita](https://ourworldindata.org/grapher/agricultural-area-per-capita)

4. [Land Use Per Protein](https://ourworldindata.org/grapher/land-use-protein-poore?country=Beef+%28dairy+herd%29~Beef+%28beef+herd%29~Cheese~Fish+%28farmed%29~Eggs~Grains~Groundnuts~Milk~Lamb+%26+Mutton~Nuts~Peas~Pig+Meat~Other+Pulses~Poultry+Meat~Tofu+%28soybeans%29~Wheat+%26+Rye~Maize~Oatmeal)





